Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-14 02_Paper/paper.tex
format
exp update.

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. All three methods are trained using standard hyperparameters, which we found to work well. \footnote{To allow exact reproduction of these results source code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

@@

It is worth to mention the most important points learned during the project implementation. This might help as building blocks for further research in the area.

@@

Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.

>>>>

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. In this case, we chose to train all three models using standard hyperparameters, which we found to work well. \footnote{To allow exact reproduction of our results source code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

@@

It is worth to mention the most important points learned during the project implementation. This might help as building blocks for further research in the area. Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.

\vspace{0.2cm}

@@
